---
title: "Eating Out"
author: "Davy D"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out.

The variable name you are looking for is "eatout".


### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS=read.csv('GSS1996.csv')
#require (haven)
```

```{r}
GSS = read.csv('GSS1996.csv')
GSS$race = as.factor(GSS$race)
GSS$eatout = as.factor(GSS$eatout)
GSS$race = case_match(GSS$race, '1'~'white', '2'~'black', '3'~"other")
GSS$eatout = case_match(GSS$eatout, '1'~'yes', '2' ~ 'no')

```

## Methods

Both 'race' and 'eatout' categorical. Therefore we use the cat~cat helper file. 

## Descriptive results

## graphical description

```{r}
barchartGC(~race + eatout,data=GSS)
barchartGC(~race + eatout,data=GSS, type="percent")
```

This barchart shows that out of all 3 races, white people eat out the most with the average of 80 percent, other is next with 70 and last black with 65 percent.  
## numerical description

```{r}
table = xtabs(~eatout + race, data=GSS)
print(table)
rowPerc(table)
colPerc(table)
```
This table shows that out of all three races white people have the average to eat out the most at 82 percent, and the other race the least with 5 percent.
## infrential results

### Chi-squared test results
```{r}
chisq.test(table)
chisqtestGC(table)
```

The chi-squared p-value is 0.0009 which is less than 0.05 which means we reject the null hypothesis that there is no difference in the amount people eat out depending on race.
### fisherXY test results
```{r}
fisher.test(table)
fisherXY(GSS$eatout,GSS$race, printAll= T)
```
The p- value for the fisher exact test is 0.00122 which is greater than 0.05 which means we fail to reject the null hypothesis. 

## Summary and Conclusions

We are able reject the null hypothesis, there is a correlation between race and the amount of how much people eat out. we are able to prove this with the fisher test and the p-value being 0.00122 which is smaller than 0.05 which is sufficient enough proof aswell as out barchart providing the proof that white people are more likely to eat out at 80% versus black, and the other race. 


